---
title: "example-5b"
output: html_document
runtime: shiny
---

This applicatio illustrate how to use shiny in an interactive RMarkdown document. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(shiny)
library(ggplot2)
```

## Plot with a drop down

The pane is split into two parts with the drop down on the left and plot on the right. I normally start constructing the layout - this is what the ui part of regular shiny app looks like. And then working out the the server part. 

```{r myplot, echo = T}
selectInput("col", "Choose numeric column to graph:", 
                  choices = c(colnames(diamonds[,sapply(diamonds, is.numeric)])))

#Now work out the output
output$diaHist = renderPlot({
    ggplot(diamonds, aes_string(x=input$col)) + geom_histogram()
})

plotOutput("diaHist")
```

## Nice Data Table

Dynamic tables in your document with [DataTables](http://rstudio.github.io/DT/) . DataTables is a wrapper around the javascript library https://datatables.net/. Don't confuse with the [data.table](https://github.com/Rdatatable/data.table/wikidata.table) library. 

```{r pressure, echo=FALSE}
library(DT)
datatable(head(diamonds,n=10)) #Be careful don't send a million rows to the browser..... 
```


